Prefetching SPARQL query cacher

### 2016-07-28 dissertation/cache-proxy.tex
space

Merging the quad plans into a single SPARQL BGP plan is not
straightforward in the presence of a quad pattern that is to be looked
up in e.g. a cache. If we assign the letters $A$, $B$, $C$ and $D$ to
quad patterns\todo{correctly expressed?}  in the order in
Example~\ref{ex:bgp4}, the initial join tree produced by parsing may
be $ ((A \bowtie B )\bowtie C) \bowtie D) $. Now, we are interested in
a plan on the form $A \bowtie BCD$ (all commutations will be
generated). To facilitate this, we employ \emph{join rotation}. A
simple example of join rotation would be this: We first generate
subplans for both $((A \bowtie B )\bowtie C) \bowtie D) $ and $ (A
\bowtie B )\bowtie (C \bowtie D) $. Then, $C$ and $D$ can be merged to
a SPARQL BGP to $ (A \bowtie B )\bowtie CD $. Another rotation can
then be performed: $ A \bowtie (B \bowtie CD) $ and then coalesced to
the final result. The planner will generate alternative plans for both
rotated and unrotated plans, and cost is estimated for both, so we
have to be careful to design the cost model to allow the rotation to
result in SPARQL BGP plans.

>>>>

Merging the quad plans into a single SPARQL BGP plan is not
straightforward in the presence of a quad pattern that is to be looked
up in e.g. a cache. If we assign the letters $A$, $B$, $C$ and $D$ to
quad patterns \todo{correctly expressed?} in the order in
Example~\ref{ex:bgp4}, the initial join tree produced by parsing may
be $ ((A \bowtie B )\bowtie C) \bowtie D) $. Now, we are interested in
a plan on the form $A \bowtie BCD$ (all commutations will be
generated). To facilitate this, we employ \emph{join rotation}. A
simple example of join rotation would be this: We first generate
subplans for both $((A \bowtie B )\bowtie C) \bowtie D) $ and $ (A
\bowtie B )\bowtie (C \bowtie D) $. Then, $C$ and $D$ can be merged to
a SPARQL BGP to $ (A \bowtie B )\bowtie CD $. Another rotation can
then be performed: $ A \bowtie (B \bowtie CD) $ and then coalesced to
the final result. The planner will generate alternative plans for both
rotated and unrotated plans, and cost is estimated for both, so we
have to be careful to design the cost model to allow the rotation to
result in SPARQL BGP plans.
